Working title: Mirkovi\'c--Vybornov fusion in Beilinson--Drinfeld Grassmannian

### 2020-12-30 main.tex
draft begun
Joels comments?

To quote \cite{baumann2020bases} the BD Grassmannian is a relative version of the affine Grassmannian where the base is the space of effective divisors on a smooth curve $C$. The choice $C = \AA^1$ ``amply satisfies our needs and offers three advantages: there is a natural global coordinate it, every \anne{$G$-torsor}{i.e. principal $G$ bundle?} on it is trivializable, and the monodromy of any local system is trivial. Formally, $\Grbd$ is the functor on the category of commutative $\CC$-algebras that assigns to an algebra $R$ the set of isomorphism classes of triples $(\vec p,V,\sigma)$ where $\vec p\in \AA^n(R)$, $V$ is a $G^\vee$-torsor over $\AA^1_R$ and $\sigma$ is a trivialization of $V$ away from $\vec p$.''

@@

@@

\section{Convolution vs BD}
% aka, our result vs MVy's results
% aka, what they do, and what they stop short of doing

@@

    Proof of Step 1: Let $\mu_1 = (\mu_{1,1}, \mu_{1,2}, ..., \mu_{1,n})$, $\mu_2 = (\mu_{2,1}, ..., \mu_{2,n})$, and $\mu = (\mu^{(1)}, \mu^{(2)}, ..., \mu^{(n)})$. Consider the matrix 
\[
\sbox0{$\begin{matrix}1&2&3\\0&1&1\\0&0&1\end{matrix}$}
A = \left[
\begin{array}{c|c|c|c|c}
    \vphantom{\usebox{0}}\makebox[\wd0]{\large $C_1$}& \begin{matrix} \\ \\ a_{12}^1 & ... & a_{12}^{\mu^{(2)}} \end{matrix} & \makebox[\wd0]{\cdots} & \makebox[\wd0]{\cdots} &  \begin{matrix} \\ \\ a_{1n}^1 & ... & a_{1n}^{\mu^{(n)}} \end{matrix} \\ \hline
     & \vphantom{\usebox{0}}\makebox[\wd0]{\large $C_2$} & \begin{matrix} \\ \\ a_{23}^1 & ... & a_{23}^{\mu^{(3)}}  \end{matrix} & \makebox[\wd0]{\cdots} & \makebox[\wd0]{\vdots} \\ \hline
     & & \vphantom{\usebox{0}}\makebox[\wd0]{\ddots} & \vphantom{\usebox{0}}\makebox[\wd0]{\ddots} & \makebox[\wd0]{\vdots} \\ \hline
     & & & C_{n-1} & \begin{matrix} \\ \\ a_{n-1,n}^1 & ... & a_{n-1,n}^{\mu^{(n)}} \end{matrix} \\ \hline
     & & & & \vphantom{\usebox{0}}\makebox[\wd0]{$C_n$}
\end{array}
\right]
\]
where $C_i$ is the $\mu^{(i)} \times \mu^{(i)}$ companion matrix of $t^{\mu_{1,i}}(t-s)^{\mu_{2,i}}$. We send this matrix to the matrix 
\[
\begin{bmatrix}
    t^{\mu_{1,1}}(t-s)^{\mu_{2,1}} \\
    -\sum_{k=1}^{\mu^{(2)}} a_{12}^k t^{k-1} & t^{\mu_{1,2}}(t-s)^{\mu_{2,2}} \\
    \vdots & \ddots & \ddots \\
    -\sum_{k=1}^{\mu^{(n)}} a_{1n}^k t^{k-1} & \cdots & -\sum_{k=1}^{\mu^{(n)}} a_{n-1,n}^k t^{k-1} & t^{\mu_{1,n}} (t-s)^{\mu_{2,n}}
\end{bmatrix}
\]
\[
= \begin{bmatrix}
    1 \\
    p_{1,2}(t) & 1 \\
    \vdots & \ddots & \ddots \\
    p_{1,n}(t) & \cdots & p_{n-1,n}(t) & 1
\end{bmatrix}
\begin{bmatrix}
    t^{\mu_{1,1}}(t-s)^{\mu_{2,1}} \\
     & \ddots \\
     & & t^{\mu_{1,n}} (t-s)^{\mu_{2,n}}
\end{bmatrix}
\]
where 
\[p_{i,j}(t) = \frac{-\sum_{k=1}^{\mu^{(j)}} a_{i,j}^k t^{k-1}} {t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}}\]
As $\mu_1$ and $\mu_2$ are dominant, we have $p_{i,j}(t) \rightarrow 0$ as $t \rightarrow \infty$ so this matrix is indeed in $G_1[t^{-1},(t-s)^{-1}]t^{\mu_1}(t-s)^{\mu_2}$.

>>>>

\jcom{Careful: you can define it over $C^n$ or $C^{(n)}$, these are two different things.}

To quote \cite{baumann2020bases} the BD Grassmannian is a relative version of the affine Grassmannian where the base is the space of effective divisors on a smooth curve $C$. The choice $C = \AA^1$ ``amply satisfies our needs and offers three advantages: there is a natural global coordinate it, every \anne{$G$-torsor}{i.e. principal $G$ bundle?} on it is trivializable, and the monodromy of any local system is trivial. Formally, $\Grbd$ is the functor on the category of commutative $\CC$-algebras that assigns to an algebra $R$ the set of isomorphism classes of triples $(\vec p,V,\sigma)$ where $\vec p\in \AA^n(R)$, $V$ is a $G^\vee$-torsor over $\AA^1_R$ and $\sigma$ is a trivialization of $V$ away from $\vec p$.''
\jcom{Yes, $G$-torsor is the same thing as a principal $G$-bundle.}

@@

\jcom{This is not correct since, you don't use all information in $ \lambda_1, \lambda_2$.  You need to describe the Jordan type of the quotients, or something equivalent.}

@@

\jcom{I think that we figured this out.  We just need to take the matrix corresponding to $ z^{\mu_1}(z-s)^{\mu_2} $ under the MVy isomorphism.}
\section{Convolution vs BD}
% aka, our result vs MVy's results
% aka, what they do, and what they stop short of doing

@@

    Proof of Step 1: Let $\mu_1 = (\mu_{1,1}, \mu_{1,2}, ..., \mu_{1,n})$, $\mu_2 = (\mu_{2,1}, ..., \mu_{2,n})$, and $\mu = (\mu^{(1)}, \mu^{(2)}, ..., \mu^{(n)})$. Consider the matrix 
% TODO: remember to uncomment Roger's matrix 
\begin{comment}
\[
\sbox0{$\begin{matrix}1&2&3\\0&1&1\\0&0&1\end{matrix}$}
A = \left[
\begin{array}{c|c|c|c|c}
    \vphantom{\usebox{0}}\makebox[\wd0]{\large $C_1$}& \begin{matrix} \\ \\ a_{12}^1 & ... & a_{12}^{\mu^{(2)}} \end{matrix} & \makebox[\wd0]{\cdots} & \makebox[\wd0]{\cdots} &  \begin{matrix} \\ \\ a_{1n}^1 & ... & a_{1n}^{\mu^{(n)}} \end{matrix} \\ \hline
     & \vphantom{\usebox{0}}\makebox[\wd0]{\large $C_2$} & \begin{matrix} \\ \\ a_{23}^1 & ... & a_{23}^{\mu^{(3)}}  \end{matrix} & \makebox[\wd0]{\cdots} & \makebox[\wd0]{\vdots} \\ \hline
     & & \vphantom{\usebox{0}}\makebox[\wd0]{\ddots} & \vphantom{\usebox{0}}\makebox[\wd0]{\ddots} & \makebox[\wd0]{\vdots} \\ \hline
     & & & C_{n-1} & \begin{matrix} \\ \\ a_{n-1,n}^1 & ... & a_{n-1,n}^{\mu^{(n)}} \end{matrix} \\ \hline
     & & & & \vphantom{\usebox{0}}\makebox[\wd0]{$C_n$}
\end{array}
\right]
\]
\end{comment}
where $C_i$ is the $\mu^{(i)} \times \mu^{(i)}$ companion matrix of $t^{\mu_{1,i}}(t-s)^{\mu_{2,i}}$. We send this matrix to the matrix 
\[
\begin{bmatrix}
    t^{\mu_{1,1}}(t-s)^{\mu_{2,1}} \\
    -\sum_{k=1}^{\mu^{(2)}} a_{12}^k t^{k-1} & t^{\mu_{1,2}}(t-s)^{\mu_{2,2}} \\
    \vdots & \ddots & \ddots \\
    -\sum_{k=1}^{\mu^{(n)}} a_{1n}^k t^{k-1} & \cdots & -\sum_{k=1}^{\mu^{(n)}} a_{n-1,n}^k t^{k-1} & t^{\mu_{1,n}} (t-s)^{\mu_{2,n}}
\end{bmatrix}
\]
\[
= \begin{bmatrix}
    1 \\
    p_{1,2}(t) & 1 \\
    \vdots & \ddots & \ddots \\
    p_{1,n}(t) & \cdots & p_{n-1,n}(t) & 1
\end{bmatrix}
\begin{bmatrix}
    t^{\mu_{1,1}}(t-s)^{\mu_{2,1}} \\
     & \ddots \\
     & & t^{\mu_{1,n}} (t-s)^{\mu_{2,n}}
\end{bmatrix}
\]
where 
\[p_{i,j}(t) = \frac{-\sum_{k=1}^{\mu^{(j)}} a_{i,j}^k t^{k-1}} {t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}}\]
As $\mu_1$ and $\mu_2$ are dominant, we have $p_{i,j}(t) \rightarrow 0$ as $t \rightarrow \infty$ so this matrix is indeed in $G_1[t^{-1},(t-s)^{-1}]t^{\mu_1}(t-s)^{\mu_2}$.
